Explore tumor cell classification with CellAssign

### 2024-05-22 analyses/cell-type-ewings/template_notebooks/02-cellassign.Rmd
save cellassign output

# output annotations
cellassign_annotations_file <- file.path(params$results_dir, glue::glue("{params$library_id}_cellassign-annotations.tsv"))
```

@@

>>>>

# output annotations
cellassign_annotations_file <- file.path(params$results_dir, glue::glue("{params$library_id}_cellassign-classifications.tsv"))
```

@@

## Save annotations

```{r}
celltype_df <- celltype_df |> 
  dplyr::select(barcodes, 
                marker_gene_cellassign_annotations = cellassign_annotations, 
                visser_cellassign_annotations, 
                panglao_cellassign_annotations)

readr::write_tsv(celltype_df, cellassign_annotations_file)
```
